---
title: "Milestone Report"
author: "Mohammad Ateya"
date: "6/3/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Data Science Capstone Week 2 Milestone Report 
### Exploratory Data Analysis

This week-2 milestone report of the data science captsone project aims at exploring the datsets which were downloaded from the course's [website](https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip). 
There are three different files in the English language database which will be explored in this analysis:

* en_US.blogs.txt
* en_US.news.txt
* en_US.twitter.txt

```{r reading the data}
library(tidyverse);library(knitr)
us_twitter <- read_lines("./final/en_US/en_US.twitter.txt")
us_blogs <- read_lines("./final/en_US/en_US.blogs.txt")
us_news <-  read_lines("./final/en_US/en_US.news.txt")
# convert to data frames:
us_twitter_df <- tibble(us_twitter)
us_blogs_df <- tibble(us_blogs)
us_news_df <- tibble(us_news)
```
#### **Display the first 6 rows of each dataset:**
``` {r exploratory analysis head}

kable(head(us_twitter_df))
kable(head(us_blogs_df))
kable(head(us_news_df))
# **Display summary of the data**
```
#### **Display the summary of each dataset:**
```{r exploratory analysis summary}
kable(cbind(summary(us_twitter_df),summary(us_blogs_df),summary(us_news_df)))
```
